Commutative Character Sheaves on smooth group schemes over finite fields

### 2016-01-27 followup.tex
Getting ready to talk to David. Moving computers.

\title[Commutative Character Sheaves]{Commutative Character Sheaves on smooth group schemes over finite fields}
%with an application to geometric types for supercuspidal representations
\author{Clifton Cunningham}
\address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Calgary, AB, Canada, {T2N~1N4}.}
\email{cunning@math.ucalgary.ca}
\author{David Roe}
\address{Department of Mathematics, University of Pittsburgh, 301 Thackeray Hall, Pittsburgh, PA , United States, 15260.}
\email{roed.math@gmail.com}

@@

\begin{proposition}\label{prop:quasicharacters}
Let $\underline{G}$ be a smooth group scheme over $\OK$.
Let $\chi : \underline{G}(\OK) \to \CC^\times$ be a quasicharacter/continuous linear character. 
The there is a Weil sheaf $\cs{L}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{L}} = \trace \chi$. \todo{Missing proof}
\end{proposition}

@@

The representations $\,^\circ \rho_i$ are defined recursively. Set $\,^\circ \rho_0 = \varrho$.
Suppose $i=0, \ldots, d-1$.
The key to defining the representation $\,^\circ\rho_{i+1}$ from $\,^\circ \rho_i$ is the following diagram.
\begin{equation}\label{eq:semiprod}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && \,^\circ K^{i}\cap J^{i+1}\arrow{d} && \\
1 \arrow{r} & J^{i+1} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d} \arrow{r} & \,^\circ K^i \arrow{r} & 1\\
&& \,^\circ K^{i+1} \arrow{d} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $\,^\circ K^i \ltimes J^{i+1}$.
Write $\inf(\,^\circ\rho_i \otimes \varphi_i)$ for the representation of $\,^\circ K^i \ltimes J^{i+1}$ obtained by pulling back $\,^\circ\rho_i$ along $\,^\circ K^i \ltimes J^{i+1} \to \,^\circ K^i$. 
By \cite{yu:01a}*{}, the representation 
\begin{equation}\label{eq:tensor}
h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)
\end{equation}
of $\,^\circ K^i \ltimes J^{i+1}$ is trivial on $\,^\circ K^{i}\cap J^{i+1}$, so $h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)$ descends to $\,^\circ K^{i+1}$. This defines $\,^\circ \rho_{i+1}$.\todo{I didn't use $\varphi_d$, so this can't be quite right.}

%The character of $\,^\circ \rho_d$ on $\,^\circ K^d = \,^\circ K = J^0 \cdots J^d$ satisfies
%\[
%\trace(\,^\circ \rho)(k_0 \cdots k_d) = \varrho(k_0)  \varphi_0(k_0) \cdots \varphi_d(k_d),
%\]
%for $k_i\in J^i$.

@@

\begin{proposition}\label{prop:geotypes}
Let $(\,^\circ K,\,^\circ \rho)$ be a Yu type.
Assume Conjecture~\ref{conj:Jacobi}.
and also that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
Let $G$ be the Greenberg transform of the smooth group scheme $\underline{G}$.
Then there is a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
\end{proposition}

@@

By continuity of the quasicharacters $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$, there is some $m \in \NN$ and a factorization
\[
\begin{tikzcd}
\underline{G}^i(\OK) \arrow{rr}{\varphi^i} \arrow{rd} && \CC^\times\\
& \underline{G}^i(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\phi^i_m} 
\end{tikzcd}
\] 
for each $i=0, \ldots d$.
Using Proposition~\ref{prop:quasicharacters}, let $\cs{L}^i_m$ be a geometrization of the linear character $\phi^i_m: \Gr^{\OK}_{m}(\underline{G}^i) \to \CC^\times$; so
\[
\trFrob{\cs{L}^i_m} = \trace \phi^i_m.
\]
%Recall that the full Greenberg transform $\Gr^{\OK}(\underline{G}^i)$ is a group scheme over $\Fq$ such that $\Gr^{\OK}(\underline{G}^i)(\Fq) = \underline{G}^i(\Fq)$, canonically, and comes equipped with a morphism $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_m(\underline{G}^i)$.
%Let $\cs{L}^i$ be the  Weil sheaf on $\Gr^{\OK}(\underline{G}^i)$ obtained from $\cs{L}^i_m$ by pullback along $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_{m}(\underline{G}^i)$. 
%Then $\cs{L}^i$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^i)$ from which the quasicharacter $\varphi^i$ may be recovered.

By \cite{lusztig:CSDG}, there is a Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
\[
\trFrob{A} = \trace \sigma.
\]
(This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.)
Let $A^+$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
Then 
\[
\trFrob{A^+} = \trace \tau.
\]
The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg $\Gr^{\OK}_0(\underline{G}^0)$\cite{CR}*{\S 4.3}. 
With $m\in \NN$ as above, let $\cs{A}_m^0$ be the pull-back of $A^0$ along the affine morphism
$\Gr^{\OK}_{m}(\underline{G}^0) \to \Gr^{\OK}_{0}(\underline{G}^0)$.
Factor
\[
\begin{tikzcd}
\underline{G}^0(\OK) \arrow{rr}{\trace(\varrho)} \arrow{rd} && \CC\\
& \underline{G}^0(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\trace(\varrho)_m} 
\end{tikzcd}
\]
Then $\cs{A}_m^0$ is a Weil sheaf on $\underline{G}^i$, from which $\trace(\varrho)_m$ may be recovered:
\[
\trFrob{\cs{A}^0_m} = \trace(\varrho)_m
\]
%Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{\OK}(\underline{G}^0) \to \Gr^{\OK}_{m}(\underline{G}^0)$.
%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^0)$ from which the character of $\varrho$ may be recovered.

@@

We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{\OK}_m(\underline{G}^{i})$, for $i=1,\ldots ,d$, recursively, following the construction of the representations $\,^0\rho_i$, reviewed in Section~\ref{ssec:review}.
We have already defined $\cs{A}^0_m$.
Suppose $\cs{A}^i_m$ on $G_m^i$ is defined; we shall construct $\cs{A}_m^{i+1}$ on $G_m^{i+1}$.

Applying the Greenberg functor $\Gr^{\OK}_m$, to \eqref{eq:pimodel} gives
\begin{equation}\label{eq:pi}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && G_m^{i}\times_{G_m} J_m^{i+1} \arrow{d} && \\
1 \arrow{r} &J_m^{i+1} \arrow{r} & G_m^i \ltimes J_m^{i+1} \arrow{d}{\pi_m^{i+1}} \arrow{r}{p_m^{i}} & G_m^i \arrow{r} & 1\\
&& G_m^{i+1} \arrow{d} && \\
&& 1 && 
\end{tikzcd}
\end{equation}
where $J_m^{i+1} \ceq \Gr^{\OK}_m(\underline{J}^{i+1})$ and $G_m^{i} \ceq \Gr^{\OK}_m(\underline{G}^{i})$
By \cite{BG-A}*{Prop 7.1}, the sequences are exact.
Consider $\cs{A}_m^{i}\otimes \cs{L}_m^{i}$ on $G_m^{i}$ and let 
\[
(p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
\]
be the Weil sheaf on $G_m^{i}\ltimes J_m^{i+1}$ obtained by pullback along $G_m^{i}\ltimes J_m^{i+1} \to G_m^{i}$.
Consider the sheaf 
\[
\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
\]
on $G_m^{i}\ltimes J_m^{i+1}$ and compare with \eqref{eq:tensor}.
With reference to the morphism $\pi_m^{i+1} : G_m^i \ltimes J_m^{i+1} \to G_m^{i+1}$ from \eqref{eq:pi}, define
\[
\cs{\tilde A}_m^{i+1} \ceq R(\pi_m^{i+1})_! (\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})).
\]
%Let $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$ and set $\cs{A}_m^{i+1} \ceq \cs{\tilde A}_m^{i+1}(-n)$ (Tate twist).
Before continuing, let us calculate: 
\begin{eqnarray*}
\trFrob{\cs{\tilde A}^{i+1}_m}(x)
&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^i)}(y)\\
&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1}}(y) \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y) ) \trFrob{\cs{L}_m^i}(p_m^{i+1}(y)).
\end{eqnarray*}
Now, 
\[
y \mapsto \trFrob{\cs{W}_m^{i+1}}(y) \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y) ) \trFrob{\cs{L}_m^i}(p_m^{i+1}(y))
\]
is precisely 
\[
\begin{tikzcd}
\end{tikzcd}
\]

>>>>

\title[Commutative Character Sheaves]{Commutative Character Sheaves on smooth group schemes over finite fields}
%with an application to geometric types for supercuspidal representations
\author{Clifton Cunningham}
\address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Calgary, Alberta, Canada, {T2N~1N4}.}
\email{cunning@math.ucalgary.ca}
\author{David Roe}
\address{Department of Mathematics, University of Pittsburgh, 301 Thackeray Hall, Pittsburgh, PA , United States, 15260.}
\email{roed.math@gmail.com}

@@

\begin{proposition}\label{prop:quasicharacters}
Let $\underline{G}$ be a smooth group scheme over $\OK$.
Let $\chi : \underline{G}(\OK) \to \EEx$ be a quasicharacter/continuous linear character. 
The there is a Weil sheaf $\cs{L}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{L}} = \trace \chi$. \todo{Missing proof}
\end{proposition}

@@

The representations $\,^\circ \rho_i$ are defined recursively. Set $\,^\circ \rho_0 = \varrho$.
Suppose $i=0, \ldots, d-1$.
The key to defining the representation $\,^\circ\rho_{i+1}$ from $\,^\circ \rho_i$ is the following diagram.
\begin{equation}\label{eq:semiprod}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && \,^\circ K^{i}\cap J^{i+1}\arrow{d} && \\
1 \arrow{r} & J^{i+1} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & \,^\circ K^i \arrow{r} & 1\\
&& \,^\circ K^{i+1} \arrow{d}{} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $\,^\circ K^i \ltimes J^{i+1}$.
Write $\inf(\,^\circ\rho_i \otimes \varphi_i)$ for the representation of $\,^\circ K^i \ltimes J^{i+1}$ obtained by pulling back $\,^\circ\rho_i$ along $\,^\circ K^i \ltimes J^{i+1} \to \,^\circ K^i$. 
Consider the representation
\begin{equation}\label{eq:tensor}
\,^0{\tilde\rho}_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)
\end{equation}
of $\,^\circ K^i \ltimes J^{i+1}$.
By construction, the character of this representation satisfies
\begin{equation}\label{eq:tilderho}
\trace(\,^0{\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(h_{i+1}(y))\ \trace(\,^\circ\rho_i)(p_i(y))\ \varphi_i(p_i(y))
\end{equation}
for $y \in \,^\circ K^i \ltimes J^{i+1}$.
By \cite{yu:01a}*{}, the representation $\,^0{\tilde\rho}_{i+1}$ of $\,^\circ K^i \ltimes J^{i+1}$ is trivial on $\,^\circ K^{i}\cap J^{i+1}$ so $\,^0{\tilde\rho}_{i+1}$ descends to $\,^\circ K^{i+1}$. 
This defines $\,^\circ \rho_{i+1}$.\todo{I didn't use $\varphi_d$, so this can't be quite right.}
%The character of $\,^\circ \rho_d$ on $\,^\circ K^d = \,^\circ K = J^0 \cdots J^d$ satisfies
%\[
%\trace(\,^\circ \rho)(k_0 \cdots k_d) = \varrho(k_0)  \varphi_0(k_0) \cdots \varphi_d(k_d),
%\]
%for $k_i\in J^i$.

@@

Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we fix, once and for all, an isomorphism $\CC \sim \EE$.

\begin{proposition}\label{prop:geotypes}
Let $(\,^\circ K,\,^\circ \rho)$ be a Yu type.
Assume Conjecture~\ref{conj:Jacobi}.
and also that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
Let $G$ be the Greenberg transform of the smooth group scheme $\underline{G}$.
Then there is a virtual Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace(\,^\circ \rho)$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
\end{proposition}

@@

By continuity of the quasicharacters $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$, there is some $m \in \NN$ and a factorization
\[
\begin{tikzcd}
\underline{G}^i(\OK) \arrow{rr}{\varphi^i} \arrow{rd} && \EEx\\
& \underline{G}^i(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\phi^i_m} 
\end{tikzcd}
\] 
for each $i=0, \ldots d$.
Using Proposition~\ref{prop:quasicharacters}, let $\cs{L}^i_m$ be a geometrization of the linear character $\phi^i_m: \Gr^{\OK}_{m}(\underline{G}^i) \to \CC^\times$; so
\[
\trFrob{\cs{L}^i_m} = \trace \phi^i_m.
\]
%Recall that the full Greenberg transform $\Gr^{\OK}(\underline{G}^i)$ is a group scheme over $\Fq$ such that $\Gr^{\OK}(\underline{G}^i)(\Fq) = \underline{G}^i(\Fq)$, canonically, and comes equipped with a morphism $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_m(\underline{G}^i)$.
%Let $\cs{L}^i$ be the  Weil sheaf on $\Gr^{\OK}(\underline{G}^i)$ obtained from $\cs{L}^i_m$ by pullback along $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_{m}(\underline{G}^i)$. 
%Then $\cs{L}^i$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^i)$ from which the quasicharacter $\varphi^i$ may be recovered.

By \cite{lusztig:CSDG}, there is a Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
\[
\trFrob{A} = \trace \sigma.
\]
(This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.)
Let $A^0$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
Then 
\[
\trFrob{A^0} = \trace \tau.
\]
The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg $\Gr^{\OK}_0(\underline{G}^0)$\cite{CR}*{\S 4.3}. 
With $m\in \NN$ as above, let $\cs{A}_m^0$ be the pull-back of $A^0$ along the affine morphism
$\Gr^{\OK}_{m}(\underline{G}^0) \to \Gr^{\OK}_{0}(\underline{G}^0)$.
Factor
\[
\begin{tikzcd}
\underline{G}^0(\OK) \arrow{rr}{\trace(\varrho)} \arrow{rd} && \EE \\
& \underline{G}^0(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\trace(\varrho)_m} 
\end{tikzcd}
\]
Then $\cs{A}_m^0$ is a Weil sheaf on $\underline{G}^i$, from which $\trace(\varrho)_m$ may be recovered:
\[
\trFrob{\cs{A}^0_m} = \trace(\varrho)_m
\]
%Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{\OK}(\underline{G}^0) \to \Gr^{\OK}_{m}(\underline{G}^0)$.
%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^0)$ from which the character of $\varrho$ may be recovered.

@@

We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{\OK}_m(\underline{G}^{i})$, for $i=1,\ldots ,d$, recursively, following the construction of the representations $\,^0\rho_i$, reviewed in Section~\ref{ssec:review}.
We have already defined $\cs{A}^0_m$ so that 
\[
\trFrob{\cs{A}^0_m} = \trace(\,^\circ \rho_0)_m
\]
where $\trace(\,^\circ \rho_0)_m : G_m^0(\Fq) \to \EE$ is defined by 
\[
\underline{G}^0
\]
and the canonical identification $G_m^0(\Fq) = \underline{G}^0(\OK/\mathfrak{p}_K^{m+1})$.

Suppose $\cs{A}^i_m$ on $G_m^i$ is defined; we shall construct $\cs{A}_m^{i+1}$ on $G_m^{i+1}$.

Applying the Greenberg functor $\Gr^{\OK}_m$, to \eqref{eq:pimodel} gives
\begin{equation}\label{eq:pi}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && G_m^{i}\times_{G_m} J_m^{i+1} \arrow{d} && \\
1 \arrow{r} &J_m^{i+1} \arrow{r} & G_m^i \ltimes J_m^{i+1} \arrow{d}{\pi_m^{i+1}} \arrow{r}{p_m^{i}} & G_m^i \arrow{r} & 1\\
&& G_m^{i+1} \arrow{d} && \\
&& 1 && 
\end{tikzcd}
\end{equation}
where $J_m^{i+1} \ceq \Gr^{\OK}_m(\underline{J}^{i+1})$ and $G_m^{i} \ceq \Gr^{\OK}_m(\underline{G}^{i})$
By \cite{BG-A}*{Prop 7.1}, the sequences are exact.
Consider $\cs{A}_m^{i}\otimes \cs{L}_m^{i}$ on $G_m^{i}$ and let 
\[
(p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
\]
be the Weil sheaf on $G_m^{i}\ltimes J_m^{i+1}$ obtained by pullback along $G_m^{i}\ltimes J_m^{i+1} \to G_m^{i}$.
Consider the sheaf 
\[
\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
\]
on $G_m^{i}\ltimes J_m^{i+1}$ and compare with \eqref{eq:tensor}.
With reference to the morphism $\pi_m^{i+1} : G_m^i \ltimes J_m^{i+1} \to G_m^{i+1}$ from \eqref{eq:pi}, define
\[
\cs{\tilde A}_m^{i+1} \ceq R(\pi_m^{i+1})_! (\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})).
\]
%Let $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$ and set $\cs{A}_m^{i+1} \ceq \cs{\tilde A}_m^{i+1}(-n)$ (Tate twist).
Before continuing, let us calculate: 
\begin{eqnarray*}
\trFrob{\cs{\tilde A}^{i+1}_m}(x)
&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^i)}(y)\\
&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1}}(y)\  \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y) )\ \trFrob{\cs{L}_m^i}(p_m^{i+1}(y)).
\end{eqnarray*}
Comparing with \eqref{eq:tilderho}, we see that 
\[
y \mapsto \trFrob{\cs{W}_m^{i+1}}(y)\ \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y))\ \trFrob{\cs{L}_m^i}(p_m^{i+1}(y))
\]
is precisely the function obtained by factoring the character of $\,^\circ {\tilde \rho}_{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$, using the canonical identification $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$. 
In particular, this is trivial on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$.
It follows that 
\[
\trFrob{\cs{\tilde A}^{i+1}_m} = n \trace(\,^\circ \rho_{i+1})
\]
on $G_m^{i+1}(\Fq)$ with $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$.\todo{Hmm... Homomorphism?}
\todo{If $n$ is a power of $q$, then we can use Tate twists to avoid working with virtual sheaves! Is $G^{i}\cap J_m^{i+1}$ unipotent? Is so, then there's a chance.}
Let $\cs{A}_m^{i+1}$ be the \emph{virtual} Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{\tilde A}_m^{i+1}$.

This completes the inductive definition of
